---
title: "Incidents - Exploratory Analysis"
author: "Lex Gourley"
date: "9/19/2021"
output: html_document
---

```{r setup, include=FALSE}
require(data.table)
require(ggplot2)
require(MASS)
require(tidyverse)
require(janitor)
require(chron)
require(stringr)
require(tm)
require(qdap)
```

## Read the data look at quick summary stats.
```{r import}

file <- "Incidents_Original_Adjusted.csv"
df <- read.csv(file,header = TRUE, stringsAsFactors = FALSE, na.strings=c("NA","N/A","","na","Na","n/a","N/a","NaN","nA"))
setDT(df)
df

# Dimension of data set
dim(df)
# Names of fields
names(df)
# Structure of fields
str(df)
# Summary of fields
summary(df)
```
## Split up CEDAR Remarks
```{r cedar}
df_2 <- separate(data=df, col=CEDAR.REMARKS, into=c("EVENTTYPE.CEDAR","STATUS.CEDAR","MORID.CEDAR","FACILITY.CEDAR","EVENTDATE.CEDAR","UTCTIME.CEDAR","UTCTIME24.CEDAR","CALENDARDATE.CEDAR","NEARESTAIRPORT.CEDAR","METAR.CEDAR","POTENTIALLYSIGNIFICANT.CEDAR","CALLSIGN.CEDAR","ACTYPE.CEDAR","IFRVFR.CEDAR","AUTHCERT.CEDAR","AIRSPACECLASS.CEDAR","ACLOCATION.CEDAR","ACALTITUDE.CEDAR","ACHEADING.CEDAR","RELATIVECLOCKPOSITION.CEDAR","UASREGISTRATIONNUM.CEDAR","UASLONG.CEDAR","UASLAT.CEDAR","UASTYPE.CEDAR","UASFORMATION.CEDAR","CLOSESTPROXIMITY.CEDAR","UASWEIGHTGT55.CEDAR","UASDIM.CEDAR","UASFWROTOR.CEDAR","UASACTIVITYRISK.CEDAR","UASCOLOR.CEDAR","PILOTREPORTEDNMAC.CEDAR","TCASRA.CEDAR","LEOCONTACT.CEDAR","SUMMARY.CEDAR","QAFINDINGS.CEDAR"),sep="; ")



df_2$EVENTTYPE.CEDAR <- gsub("CEDAR – Event Type: ","",df_2$EVENTTYPE.CEDAR)
df_2$STATUS.CEDAR <- gsub("Status: ","",df_2$STATUS.CEDAR)
df_2$MORID.CEDAR <- gsub("MOR ID: ","",df_2$MORID.CEDAR)
df_2$FACILITY.CEDAR <- gsub("Facility: ","",df_2$FACILITY.CEDAR)
df_2$EVENTDATE.CEDAR <- gsub("Event Date: ","",df_2$EVENTDATE.CEDAR)
df_2$UTCTIME.CEDAR <- gsub("UTC Time: ","",df_2$UTCTIME.CEDAR)
df_2$UTCTIME24.CEDAR <- gsub("UTC Time 24 HR Format: ","",df_2$UTCTIME24.CEDAR)
df_2$CALENDARDATE.CEDAR <- gsub("Calendar Date: ","",df_2$CALENDARDATE.CEDAR)
df_2$NEARESTAIRPORT.CEDAR <- gsub("Nearest Airport: ","",df_2$NEARESTAIRPORT.CEDAR)
df_2$METAR.CEDAR <- gsub("METAR: ","",df_2$METAR.CEDAR)
df_2$POTENTIALLYSIGNIFICANT.CEDAR <- gsub("Potentially Significant: ","",df_2$POTENTIALLYSIGNIFICANT.CEDAR)
df_2$CALLSIGN.CEDAR <- gsub("Callsign: ","",df_2$CALLSIGN.CEDAR)
df_2$ACTYPE.CEDAR <- gsub("A/C Type: ","",df_2$ACTYPE.CEDAR)
df_2$IFRVFR.CEDAR <- gsub("IFR / VFR: ","",df_2$IFRVFR.CEDAR)
df_2$AUTHCERT.CEDAR <- gsub("Certificate of Authorization: ","",df_2$AUTHCERT.CEDAR)
df_2$AIRSPACECLASS.CEDAR <- gsub("Airspace Class: ","",df_2$AIRSPACECLASS.CEDAR)
df_2$ACLOCATION.CEDAR <- gsub("A/C Location F/R/D: ","",df_2$ACLOCATION.CEDAR)
df_2$ACALTITUDE.CEDAR <- gsub("A/C Altitude: ","",df_2$ACALTITUDE.CEDAR)
df_2$ACHEADING.CEDAR <- gsub("A/C Heading: ","",df_2$ACHEADING.CEDAR)
df_2$RELATIVECLOCKPOSITION.CEDAR <- gsub("Relative Clock Position: ","",df_2$RELATIVECLOCKPOSITION.CEDAR)
df_2$UASREGISTRATIONNUM.CEDAR <- gsub("UAS Registration #: ","",df_2$UASREGISTRATIONNUM.CEDAR)
df_2$UASLONG.CEDAR <- gsub("UAS Longitude: ","",df_2$UASLONG.CEDAR)
df_2$UASLAT.CEDAR <- gsub("UAS Latitude: ","",df_2$UASLAT.CEDAR)
df_2$UASTYPE.CEDAR <- gsub("UAS Type: ","",df_2$UASTYPE.CEDAR)
df_2$UASFORMATION.CEDAR <- gsub("UAS Formation: ","",df_2$UASFORMATION.CEDAR)
df_2$CLOSESTPROXIMITY.CEDAR <- gsub("Closest Proximity (feet): ","",df_2$CLOSESTPROXIMITY.CEDAR)
df_2$UASWEIGHTGT55.CEDAR <- gsub("UAS Weight Exceeds 55lbs: ","",df_2$UASWEIGHTGT55.CEDAR)
df_2$UASDIM.CEDAR <- gsub("UAS Dimensions (feet): ","",df_2$UASDIM.CEDAR)
df_2$UASFWROTOR.CEDAR <- gsub("UAS Fixed Wing/Rotorcraft: ","",df_2$UASFWROTOR.CEDAR)
df_2$UASACTIVITYRISK.CEDAR <- gsub("UAS Activity Risk: ","",df_2$UASACTIVITYRISK.CEDAR)
df_2$UASCOLOR.CEDAR <- gsub("UAS Color: ","",df_2$UASCOLOR.CEDAR)
df_2$PILOTREPORTEDNMAC.CEDAR <- gsub("Pilot Reported as NMAC: ","",df_2$PILOTREPORTEDNMAC.CEDAR)
df_2$TCASRA.CEDAR <- gsub("TCAS RA: ","",df_2$TCASRA.CEDAR)
df_2$LEOCONTACT.CEDAR <- gsub("Law Enforcement Contact Info: ","",df_2$LEOCONTACT.CEDAR)
df_2$SUMMARY.CEDAR <- gsub("Summary: ","",df_2$SUMMARY.CEDAR)
df_2$QAFINDINGS.CEDAR <- gsub("QA Findings: ","",df_2$QAFINDINGS.CEDAR)
```

## Check for null values and duplicates
```{r nulls}
# Count number of nulls in each field
sapply(df_2, function(x) sum(is.na(x)))

# Count number of unique values in each field
sapply(df_2, function (x) length(unique(x)))

# Count number of duplicates. The other columns shouldn't matter if there are duplicates.
n_dup_date <- data.frame(table(df_2$DATE))
n_dup_date <- n_dup_date[n_dup_date$Freq >1,]
sum(n_dup_date$Freq) - nrow(n_dup_date)

n_dup_remarks <- data.frame(table(df_2$REMARKS))
n_dup_remarks <- n_dup_remarks[n_dup_remarks$Freq >1,]
sum(n_dup_remarks$Freq) - nrow(n_dup_remarks)
```
## General Cleaning
```{r nulls_2}
# removal of columns that are completely empty
df_2 <- df_2[,c("IMPACTEDFACILITY","OPLVL","UASTYPE.CEDAR","UASACTIVITYRISK.CEDAR","LEOCONTACT.CEDAR"):=NULL]

# removal of unnecessary columns
df_2 <- df_2[,c("ACTYPE","ORIGIN","DEST","DESTNEW"):=NULL]
df_2 <- df_2[,c("EVENTTYPE.CEDAR","STATUS.CEDAR","EVENTDATE.CEDAR","METAR.CEDAR","POTENTIALLYSIGNIFICANT.CEDAR","CALLSIGN.CEDAR","ACTYPE.CEDAR","IFRVFR.CEDAR","AUTHCERT.CEDAR","UASREGISTRATIONNUM.CEDAR","UASFORMATION.CEDAR","CLOSESTPROXIMITY.CEDAR","UASWEIGHTGT55.CEDAR","UASDIM.CEDAR","UASFWROTOR.CEDAR","UASCOLOR.CEDAR","PILOTREPORTEDNMAC.CEDAR","TCASRA.CEDAR"):=NULL]

# fill in null rows in SECONDARYCODES temporarily
df_2$SECONDARYCODES[is.na(df_2$SECONDARYCODES)] <- "N/A"

# removal of rows with codes unnecessary to project
df_2 <- df_2[!grepl("ADMIN",df_2$PRIMARYCODE)]
df_2 <- df_2[!grepl("AIRCRAFT ACCIDENT",df_2$PRIMARYCODE)]
df_2 <- df_2[!grepl("AIRPORT",df_2$PRIMARYCODE)]
df_2 <- df_2[!grepl("ATC FACILITY",df_2$PRIMARYCODE)]
df_2 <- df_2[!grepl("C-UAS",df_2$PRIMARYCODE)]
df_2 <- df_2[!grepl("DISTURB",df_2$PRIMARYCODE)]
df_2 <- df_2[!grepl("EQUIPMENT",df_2$PRIMARYCODE)]
df_2 <- df_2[!grepl("HORNET",df_2$PRIMARYCODE)]
df_2 <- df_2[!grepl("NORDO",df_2$PRIMARYCODE)]
df_2 <- df_2[!grepl("VIP",df_2$PRIMARYCODE)]
df_2 <- df_2[!grepl("WAIVER",df_2$PRIMARYCODE)]
df_2 <- df_2[!grepl("WASP",df_2$PRIMARYCODE)]

df_2 <- df_2[!grepl("WAIVER",df_2$SECONDARYCODES)]
df_2 <- df_2[!(df_2$SECONDARYCODES=="AIRPORT")]
df_2 <- df_2[!(df_2$SECONDARYCODES=="ATC FACILITY")]
df_2 <- df_2[!grepl("C-UAS",df_2$SECONDARYCODES)]

# standardize ACFT vs Aircraft
df_2$REMARKS <- gsub("ACFT","Aircraft",df_2$REMARKS)

df_2$SECONDARYCODES[df_2$SECONDARYCODES == "N/A"] <- NA

# remove pii
df_2$REMARKS <- gsub("(\\+\\d{1,2}\\s?)?1?\\-?\\.?\\s?\\(?\\d{3}\\)?[\\s.-]?\\d{3}[\\s.-]?\\d{4}","",df_2$REMARKS)

df_2$REMARKS <- gsub("(NM)([A-Z]{1,3})","\\1 \\2",df_2$REMARKS)
df_2$REMARKS <- gsub("([0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*)(NM)","\\1 \\2",df_2$REMARKS)
df_2$REMARKS <- gsub("(of)([A-Z]{3,4})","\\1 \\2",df_2$REMARKS)
df_2$REMARKS <- gsub("([A-Z]{1,3})(of)","\\1 \\2",df_2$REMARKS)
df_2$REMARKS <- gsub("([A-Z]{1,3})(\\s[A-Z]{3,4}$)","\\1 of\\2",df_2$REMARKS)
df_2$REMARKS <- gsub("(RWY)([0-9]{1,2}[L|R|C]?)","\\1 \\2",df_2$REMARKS)
df_2$REMARKS <- gsub("(RWY\\s)(\\d(?!\\d))","\\10\\2",df_2$REMARKS,perl=T)
df_2$REMARKS <- gsub("south","S",df_2$REMARKS)
df_2$REMARKS <- gsub("east","E",df_2$REMARKS)
df_2$REMARKS <- gsub("north","N",df_2$REMARKS)
df_2$REMARKS <- gsub("west","W",df_2$REMARKS)
df_2$REMARKS <- gsub("South","S",df_2$REMARKS)
df_2$REMARKS <- gsub("East","E",df_2$REMARKS)
df_2$REMARKS <- gsub("North","N",df_2$REMARKS)
df_2$REMARKS <- gsub("West","W",df_2$REMARKS)
```

## Adjust date column to be readable as date/time
```{r date}
dt <- df_2$DATE
dtparts <- t(as.data.frame(strsplit(dt,"T")))
dtparts[,2] <- substr(dtparts[,2],1,5)
dateonly <- dtparts[,1]
timeonly <- dtparts[,2]

df_3 <- cbind(timeonly,df_2)
df_3 <- cbind(dateonly,df_3)
df_3$dateonly <- as.Date(df_3$dateonly)
str(df_3)
```
## Find standard format remarks
```{r standard}
df_stob <- df_3[grepl("Aircraft observed a",df_3$REMARKS)]
df_stre <- df_3[grepl("Aircraft reported a",df_3$REMARKS)]

df_4 <- rbind(df_stob,df_stre)

# group the non-standard format ones together
df_nstob <- df_3[!grepl("Aircraft observed a",df_3$REMARKS)]
df_nstre <- df_nstob[!grepl("Aircraft reported a",df_nstob$REMARKS)]
df_5 <- df_nstre
```

## Write to CSV
```{r print}
write.csv(df_3,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\00-Incidents_Cleaned.csv",row.names=FALSE)
write.csv(df_4,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\01-Incidents_Cleaned_Standard.csv",row.names=FALSE)
write.csv(df_5,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\02-Incidents_Cleaned_NonStandard.csv",row.names=FALSE)
```

## Determining if CEDAR is useful for this analysis
```{r regex}

# take the rows that have CEDAR remarks
df_cedar <- na.omit(df_3, "SUMMARY.CEDAR")

#find REMARKS that follow standard format
nm_stand <- str_extract(df_cedar$REMARKS,'[0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*(\\s*(nm|NM|miles|MILES)\\s*)(NORTH|SOUTH|EAST|WEST|(N|n)orth|(S|s)outh|(E|e)ast|(W|w)est|N|S|E|W|n|s|e|w|NW|NE|SW|SE|nw|ne|sw|se|SSE|SSW|SNE|SNW|NNE|NSE|NNE|NNW|WSW|WNW|WSE|WNE|ENE|ESE|ESW|ENW|sse|ssw|sne|snw|nne|nnw|wsw|wnw|wse|wne|ene|ese|esw|enw)*(\\s*(of|OF)\\s*[A-Z]{1,4}[0-9]{0,2})?')
nm_stand

# Cedar Records that give us NM
nm_cedar1 <- str_extract(df_cedar$SUMMARY.CEDAR,'[0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*(\\s*(nm|NM|miles|MILES)\\s*)(NORTH|SOUTH|EAST|WEST|north|south|east|west|N|S|E|W|n|s|e|w|NW|NE|SW|SE|nw|ne|sw|se|SSE|SSW|SNE|SNW|NNE|NSE|NNE|NNW|WSW|WNW|WSE|WNE|ENE|ESE|ESW|ENW|sse|ssw|sne|snw|nne|nnw|wsw|wnw|wse|wne|ene|ese|esw|enw)*(\\s*(of|OF)\\s*[A-Z]{1,4}[0-9]{0,2})?')

df_cedar_output <- cbind(df_cedar$REMARKS,nm_stand,df_cedar$SUMMARY.CEDAR,nm_cedar1,df_cedar$UASLAT.CEDAR,df_cedar$UASLONG.CEDAR)
write.csv(df_cedar_output,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\CEDAR_Output.csv",row.names=FALSE)

nm_cedar2 <- str_extract(df_cedar$SUMMARY.CEDAR,'[0-9]*\\-*[0-9]*\\.*[0-9]\\.*[0-9]*(\\s*(miles|MILES)+\\s*)(NORTH|SOUTH|EAST|WEST|north|(S|s)outh|east|west|N|S|E|W|NW|NE|SW|SE|SSE|SSW|SNE|SNW|NNE|NSE|NNE|NNW|WSW|WNW|WSE|WNE|ENE|ESE|ESW|ENW)*(\\s*(of|OF)\\s*[A-Z]{3,})?')

```

## Running extraction on whole dataset
```{r whole}

#use clean dataset of all records:
rmks <- df_3

#Total Count of Remarks in SkyWatch per Year
rmks$year <- year(rmks$dateonly)
rmks %>% count(year)

#To compare, Standard Remarks in SkyWatch per Year
df_4$year <- year(df_4$dateonly)
df_4 %>% count(year)

```

```{r initial extract location information from remarks}

# rmks <- df_3 #8633
# 
# # Extract all locations marked VOR (to use NAVAID dataset)
# pattern <- c("VOR","vor")
# rmks_vor <- rmks[grep(paste(pattern,collapse="|"),rmks$REMARKS)] #70 (DIVE DEEPER IN {r vor}) ##DONE
# rmks <- rmks[!grep(paste(pattern,collapse="|"),rmks$REMARKS)]    #8563
# 
# # Extract all locations marked RWY (to use RUNWAY dataset)
# rmks_rwy <- rmks[grepl("RWY",rmks$REMARKS)] #1239 (DIVE DEEPER in {r rwy})
# rmks <- rmks[!grepl("RWY",rmks$REMARKS)] #7324 (DIVE DEEPER)
# 
# write.csv(rmks_rwy,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\05-Incidents_Regex_RWY.csv",row.names=FALSE)
# 
# # Attempt to find XXX NM XXX of XXX format (OUT OF 7324)
# rmks$UASLOCATION <- str_extract(rmks$REMARKS,'[0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*\\s?(nm|NM)\\s? (NORTH|SOUTH|EAST|WEST|(N|n)orth|(S|s)outh|(E|e)ast|(W|w)est|N|S|E|W|n|s|e|w|NW|NE|SW|SE|nw|ne|sw|se|SSE|SSW|SNE|SNW|NNE|NSE|NNE|NNW|WSW|WNW|WSE|WNE|ENE|ESE|ESW|ENW|sse|ssw|sne|snw|nne|nnw|wsw|wnw|wse|wne|ene|ese|esw|enw)*(\\s?(of|OF)\\s?[A-Z]{3,4})')
# 
# # Extract all NA locations (OUT OF 8563)
# rmks_na <- rmks[is.na(rmks$UASLOCATION)] #3142 (DIVE DEEPER in {r nonstandard}
#   write.csv(rmks_na,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\03-Incidents_Regex_AIRPORT_NEEDSMODIFIED.csv",row.names=FALSE) #3142
# rmks <- rmks[!is.na(rmks$UASLOCATION)] #4182
#   rmks$DATASET <- "AIRPORT"
#   #Remove Duplicates (same sighting/different callsign or time)
#   rmks <- distinct(rmks,dateonly,UASLOCATION,.keep_all=TRUE) #4104
#   write.csv(rmks,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\3.1-Incidents_Regex_AIRPORT_FULLFORMAT.csv",row.names=FALSE) #4104 (DONE: LINK TO AIRPORTS FOR NEXT STEP)

```

## NONSTANDARD data
```{r nonstandard}
# 
# rmks_na2 <- rmks_na 
#   rmks_na2$DATASET <- "AIRPORT"
# 
#   # Attempt to find XXX NM XXX of XXX format (OUT OF 3142)
#   rmks_na2$UASLOCATION <- str_extract(rmks_na2$REMARKS,'[0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*\\s?(nm|NM)\\s? (NORTH|SOUTH|EAST|WEST|(N|n)orth|(S|s)outh|(E|e)ast|(W|w)est|N|S|E|W|n|s|e|w|NW|NE|SW|SE|nw|ne|sw|se|SSE|SSW|SNE|SNW|NNE|NSE|NNE|NNW|WSW|WNW|WSE|WNE|ENE|ESE|ESW|ENW|sse|ssw|sne|snw|nne|nnw|wsw|wnw|wse|wne|ene|ese|esw|enw)(\\s?[A-Z]{3,4})')
#   # Extract all NA locations (OUT OF 3179)
#   rmks_na3 <- rmks_na2[!is.na(rmks_na2$UASLOCATION)]    #96
#     rmks_nonstd_completed <- rmks_na3 #96
#   
# ##---->       NON-STANDARD DATASET (missing "of")##
#     write.csv(rmks_na3,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\3.2-Incidents_Regex_AIRPORT_NONSTD_SET1.csv",row.names=FALSE) #96
# 
#   rmks_na3_na <- rmks_na2[is.na(rmks_na2$UASLOCATION)]  #3046 (DIVE DEEPER)
#   # Attempt to find XXX NM XXX of XXX format (OUT OF 3142)
#   rmks_na3_na$UASLOCATION <- str_extract(rmks_na3_na$REMARKS,'[0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*\\s? (NORTH|SOUTH|EAST|WEST|(N|n)orth|(S|s)outh|(E|e)ast|(W|w)est|N|S|E|W|n|s|e|w|NW|NE|SW|SE|nw|ne|sw|se|SSE|SSW|SNE|SNW|NNE|NSE|NNE|NNW|WSW|WNW|WSE|WNE|ENE|ESE|ESW|ENW|sse|ssw|sne|snw|nne|nnw|wsw|wnw|wse|wne|ene|ese|esw|enw)(\\s?(of|OF)\\s?[A-Z]{3,4})')
#   # Extract all NA locations (OUT OF 3179)
#   rmks_na4 <- rmks_na3_na[!is.na(rmks_na3_na$UASLOCATION)]    #173
#     rmks_nonstd_completed <- rbind(rmks_nonstd_completed,rmks_na4) #269
#   
# ##---->       NON-STANDARD DATASET (missing "NM")##
#     write.csv(rmks_na4,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\3.3-Incidents_Regex_AIRPORT_NONSTD_SET2.csv",row.names=FALSE) #96  
#   
#   rmks_na4_na <- rmks_na3_na[is.na(rmks_na3_na$UASLOCATION)]    #2873 (DIVE DEEPER)
#   # Attempt to find XXX NM XXX of XXX format (OUT OF 2873)
#   rmks_na4_na$UASLOCATION <- str_extract(rmks_na4_na$REMARKS,'[0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*\\s?(nm|NM)\\s? (NORTH|SOUTH|EAST|WEST|(N|n)orth|(S|s)outh|(E|e)ast|(W|w)est|N|S|E|W|n|s|e|w|NW|NE|SW|SE|nw|ne|sw|se|SSE|SSW|SNE|SNW|NNE|NSE|NNE|NNW|WSW|WNW|WSE|WNE|ENE|ESE|ESW|ENW|sse|ssw|sne|snw|nne|nnw|wsw|wnw|wse|wne|ene|ese|esw|enw)')
#   # Extract all NA locations (OUT OF 2940)
#   rmks_na5 <- rmks_na4_na[!is.na(rmks_na4_na$UASLOCATION)]    #409
#     rmks_na5$UASLOCATION <- paste(rmks_na5$UASLOCATION,"of",rmks_na5$REPORTINGFACILITY)
#     rmks_nonstd_completed <- rbind(rmks_nonstd_completed,rmks_na5) #678
#     
# #!!!!!!!##---->       NON-STANDARD DATASET (TAKEN FROM REPORTING FACILITY:: NEEDS IMMEDIATE ATTENTION FOR CLEANING)##
#     write.csv(rmks_na5,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\3.4-Incidents_Regex_AIRPORT_NONSTD_SET3.csv",row.names=FALSE) #409
#     
#   rmks_na5_na <- rmks_na4_na[is.na(rmks_na4_na$UASLOCATION)]    #2464
#     # Attempt to find XXX NM XXX of XXX format (OUT OF 2464)
#     rmks_na5_na$UASLOCATION <- str_extract(rmks_na5_na$REMARKS,'[0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*\\s?((M|m)iles|MILES)\\s?(NORTH|SOUTH|EAST|WEST|(N|n)orth|(S|s)outh|(E|e)ast|(W|w)est|N|S|E|W|n|s|e|w|NW|NE|SW|SE|nw|ne|sw|se|SSE|SSW|SNE|SNW|NNE|NSE|NNE|NNW|WSW|WNW|WSE|WNE|ENE|ESE|ESW|ENW|sse|ssw|sne|snw|nne|nnw|wsw|wnw|wse|wne|ene|ese|esw|enw)(\\s?(of|OF)*\\s?)([A-Z]{3,5})')
#     # Extract all NA locations (OUT OF 2940)
#   rmks_na6 <- rmks_na5_na[!is.na(rmks_na5_na$UASLOCATION)]    #127
#     rmks_nonstd_completed <- rbind(rmks_nonstd_completed,rmks_na6)
#   rmks_na6_na <- rmks_na5_na[is.na(rmks_na5_na$UASLOCATION)]    #2337  
# 
# write.csv(rmks_na6_na,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\3.5-Incidents_Regex_AIRPORT_NONSTD_SET4.csv",row.names=FALSE)

```

## VOR data
```{r vor}
# rmks_vor2 <- rmks_vor
# 
# # Extract all locations marked RWY (to use RUNWAY dataset)
# rmks_vor_rwy <- rmks_vor2[grepl("RWY",rmks_vor2$REMARKS)] #4 (DIVE DEEPER)
#   # Attempt to find XXX NM XXX of XXX format (OUT OF 4)
#   rmks_vor_rwy$REMARKS <- gsub("Wiregrass","RRS",rmks_vor_rwy$REMARKS) #VOR CODE
#   rmks_vor_rwy$REMARKS <- gsub("Penn Cove","CVV",rmks_vor_rwy$REMARKS) #VOR CODE
#   rmks_vor_rwy$UASLOCATION <- str_extract(rmks_vor_rwy$REMARKS,'[0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*\\s?(nm|NM)\\s? (NORTH|SOUTH|EAST|WEST|(N|n)orth|(S|s)outh|(E|e)ast|(W|w)est|N|S|E|W|n|s|e|w|NW|NE|SW|SE|nw|ne|sw|se|SSE|SSW|SNE|SNW|NNE|NSE|NNE|NNW|WSW|WNW|WSE|WNE|ENE|ESE|ESW|ENW|sse|ssw|sne|snw|nne|nnw|wsw|wnw|wse|wne|ene|ese|esw|enw)*(\\s?(of|OF)\\s?[A-Z]{3,5})')
#   rmks_vor_rwy$RWYLOCATION <- str_extract(rmks_vor_rwy$REMARKS,'RWY\\s?[0-9]{2}[L|R]?')
#   rmks_vor_rwy$DATASET <- "NAVAID/RUNWAY"
#   # Extract all NA locations (OUT OF 4)
#   rmks_vor_rwy_completed <- rmks_vor_rwy[!is.na(rmks_vor_rwy$UASLOCATION)]   #1
#   rmks_vor_rwy_na <- rmks_vor_rwy[is.na(rmks_vor_rwy$UASLOCATION)]           #3 (DIVE DEEPER)
#     rmks_vor_rwy_na$UASLOCATION <- str_extract(rmks_vor_rwy_na$REMARKS,'([A-Z]{3,5})(\\sVOR)')
#   
# ##---->       VOR with RUNWAYS DATASET##
#   rmks_vor_rwy_completed <- rbind(rmks_vor_rwy_completed,rmks_vor_rwy_na)
# #    rmks_vor_rwy_completed$RWYLOCATION <- gsub("(RWY)([0-9]{2})","\\1 \\2",rmks_vor_rwy_completed$RWYLOCATION)
#   write.csv(rmks_vor_rwy_completed,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\4.2-Incidents_Regex_VOR_RWY.csv",row.names=FALSE)
# 
# rmks_vor2 <- rmks_vor2[!grepl("RWY",rmks_vor2$REMARKS)]   #66
#   # Attempt to find XXX NM XXX of XXX format (OUT OF 66)
#   rmks_vor2$UASLOCATION <- str_extract(rmks_vor2$REMARKS,'[0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*\\s?(nm|NM)\\s? (NORTH|SOUTH|EAST|WEST|(N|n)orth|(S|s)outh|(E|e)ast|(W|w)est|N|S|E|W|n|s|e|w|NW|NE|SW|SE|nw|ne|sw|se|SSE|SSW|SNE|SNW|NNE|NSE|NNE|NNW|WSW|WNW|WSE|WNE|ENE|ESE|ESW|ENW|sse|ssw|sne|snw|nne|nnw|wsw|wnw|wse|wne|ene|ese|esw|enw)*(\\s?(of|OF)\\s?[A-Z]{3,5})')
#   rmks_vor2$DATASET <- "NAVAID"
#   # Extract all NA locations (OUT OF 66)
#   rmks_vor_completed <- rmks_vor2[!is.na(rmks_vor2$UASLOCATION)]   #33 (GOOD TO GO)
#   rmks_vor2_na <- rmks_vor2[is.na(rmks_vor2$UASLOCATION)]          #33 (DIVE DEEPER)
#     # Attempt to find XXX NM XXX (of) XXX format (modified)
#     rmks_vor2_na$REMARKS <- gsub("Broadway","BWZ",rmks_vor2_na$REMARKS) #VOR CODE
#     rmks_vor2_na$REMARKS <- gsub("Calverton","CCC",rmks_vor2_na$REMARKS) #VOR CODE
#     rmks_vor2_na$REMARKS <- gsub("Wasatch","TCH",rmks_vor2_na$REMARKS) #VOR CODE
#     rmks_vor2_na$REMARKS <- gsub("the TRV","TRV",rmks_vor2_na$REMARKS) #VOR CODE
#     rmks_vor2_na$REMARKS <- gsub("Morgantown","of MGW",rmks_vor2_na$REMARKS) #VOR CODE
#     rmks_vor2_na$REMARKS <- gsub("Dolphin","DHP",rmks_vor2_na$REMARKS) #VOR CODE
#     rmks_vor2_na$REMARKS <- gsub("the Squaw Valley, CA \\(SWR\\)","SWR",rmks_vor2_na$REMARKS) #VOR CODE
#     rmks_vor2_na$REMARKS <- gsub("Solberg","SBJ",rmks_vor2_na$REMARKS) #VOR CODE
#     rmks_vor2_na$UASLOCATION <- str_extract(rmks_vor2_na$REMARKS,'[0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*\\s?(nm|NM)\\s?(NORTH|SOUTH|EAST|WEST|(N|n)orth|(S|s)outh|(E|e)ast|(W|w)est|N|S|E|W|n|s|e|w|NW|NE|SW|SE|nw|ne|sw|se|SSE|SSW|SNE|SNW|NNE|NSE|NNE|NNW|WSW|WNW|WSE|WNE|ENE|ESE|ESW|ENW|sse|ssw|sne|snw|nne|nnw|wsw|wnw|wse|wne|ene|ese|esw|enw)(\\s?(of|OF)*\\s?)([A-Z]{3,5})')
#     # Extract all NA locations (OUT OF 33)
#     rmks_vor3 <- rmks_vor2_na[!is.na(rmks_vor2_na$UASLOCATION)]    #12
#       rmks_vor3$UASLOCATION <- gsub("south","S",rmks_vor3$UASLOCATION)
#       rmks_vor3$UASLOCATION <- gsub("([0-9]*[0-9]NM\\s?)([A-Z]{1,3}\\s)([A-Z]{3,5})","\\1\\2of \\3",rmks_vor3$UASLOCATION)
#       rmks_vor_completed <- rbind(rmks_vor_completed,rmks_vor3) #45
#       
# ##---->       VOR with FULL FORMAT DATASET##
#       write.csv(rmks_vor_completed,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\4.1-Incidents_Regex_VOR_FULLFORMAT.csv",row.names=FALSE)
#       
#     rmks_vor3_na <- rmks_vor2_na[is.na(rmks_vor2_na$UASLOCATION)] #21 (DIVE DEEPER)
#       # Attempt to find XXX miles XXX (of) XXX format (modified)
#       rmks_vor3_na$REMARKS <- gsub("Fairfield","FFU",rmks_vor3_na$REMARKS) #VOR CODE
#       rmks_vor3_na$UASLOCATION <- str_extract(rmks_vor3_na$REMARKS,'[0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*\\s?((M|m)iles|MILES)\\s?(NORTH|SOUTH|EAST|WEST|(N|n)orth|(S|s)outh|(E|e)ast|(W|w)est|N|S|E|W|n|s|e|w|NW|NE|SW|SE|nw|ne|sw|se|SSE|SSW|SNE|SNW|NNE|NSE|NNE|NNW|WSW|WNW|WSE|WNE|ENE|ESE|ESW|ENW|sse|ssw|sne|snw|nne|nnw|wsw|wnw|wse|wne|ene|ese|esw|enw)(\\s?(of|OF)*\\s?)([A-Z]{3,5})')
#       # Extract all NA locations (OUT OF 29)
#       rmks_vor4 <- rmks_vor3_na[!is.na(rmks_vor3_na$UASLOCATION)]    #2
#         rmks_vor4$UASLOCATION <- gsub("([0-9]*[0-9]\\s?miles\\s?)([A-Z]{1,3}\\s)([A-Z]{3,5})","\\1\\2of \\3",rmks_vor4$UASLOCATION)
#         rmks_vor_completed <- rbind(rmks_vor_completed,rmks_vor4) #47
#         
# ##---->       VOR with MILES##
#         write.csv(rmks_vor4,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\4.3-Incidents_Regex_VOR_MILES.csv",row.names=FALSE)        
#         
#       rmks_vor4_na <- rmks_vor3_na[is.na(rmks_vor3_na$UASLOCATION)] #19 (DIVE DEEPER)
#         # Attempt to find XXX miles XXX (of) (XXX) format (modified)
#         rmks_vor4_na$REMARKS <- gsub("Shafter","MIT",rmks_vor4_na$REMARKS) #VOR CODE
#         rmks_vor4_na$REMARKS <- gsub("Treasure","TRV",rmks_vor4_na$REMARKS) #VOR CODE
#         rmks_vor4_na$UASLOCATION <- str_extract(rmks_vor4_na$REMARKS,'[0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*\\s?(NORTH|SOUTH|EAST|WEST|(N|n)orth|(S|s)outh|(E|e)ast|(W|w)est|N|S|E|W|n|s|e|w|NW|NE|SW|SE|nw|ne|sw|se|SSE|SSW|SNE|SNW|NNE|NSE|NNE|NNW|WSW|WNW|WSE|WNE|ENE|ESE|ESW|ENW|sse|ssw|sne|snw|nne|nnw|wsw|wnw|wse|wne|ene|ese|esw|enw)(\\s?(of|OF)*\\s?)([A-Z]{3,5})')
#         # Extract all NA locations (OUT OF 19)
#         rmks_vor5 <- rmks_vor4_na[!is.na(rmks_vor4_na$UASLOCATION)]    #3
#         rmks_vor_completed <- rbind(rmks_vor_completed,rmks_vor5) #50
#           
# ##---->       VOR with NONM##
#         write.csv(rmks_vor5,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\4.4-Incidents_Regex_VOR_NONM.csv",row.names=FALSE)
#           
#         rmks_vor5_na <- rmks_vor4_na[is.na(rmks_vor4_na$UASLOCATION)] #16 (DIVE DEEPER)
#           rmks_vor5_na$REMARKS <- gsub("Sea Isle VORTAC","SIE VOR",rmks_vor5_na$REMARKS) #VOR CODE
#           rmks_vor5_na$REMARKS <- gsub("Cowboy","CVE",rmks_vor5_na$REMARKS) #VOR CODE
#           rmks_vor5_na$REMARKS <- gsub("OCN, Oceanside","OCN",rmks_vor5_na$REMARKS) #VOR CODE
#           rmks_vor5_na$REMARKS <- gsub("ofDPA","DPA",rmks_vor5_na$REMARKS) #VOR CODE
#           rmks_vor5_na$REMARKS <- gsub("Yardley VOR \\(ADR\\)","ADR VOR",rmks_vor5_na$REMARKS) #VOR CODE
#           rmks_vor5_na$REMARKS <- gsub("MLFVOR","MLF VOR",rmks_vor5_na$REMARKS) #VOR CODE
#           rmks_vor5_na$REMARKS <- gsub("PZD, Pecan","PZD",rmks_vor5_na$REMARKS) #VOR CODE
#           rmks_vor5_na$UASLOCATION <- str_extract(rmks_vor5_na$REMARKS,'([A-Z]{3,5})(\\sVOR)')
#           
# ##---->       VOR with VICINITYONLY##
#           write.csv(rmks_vor5_na,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\4.5-Incidents_Regex_VOR_VICINITYONLY.csv",row.names=FALSE)
#           
#           rmks_vor_completed <- rbind(rmks_vor_completed,rmks_vor5_na) #66
#           rmks_vor_completed <- rbind(rmks_vor_completed,rmks_vor_rwy_completed, fill=TRUE)
# 
# rmks_vor_completed <- arrange(rmks_vor_completed,DATE)
# #Remove Duplicates (same sighting/different callsign or time)
# rmks_vor_completed <- distinct(rmks_vor_completed,dateonly,UASLOCATION,.keep_all=TRUE) #68
#         
# write.csv(rmks_vor_completed,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\04-Incidents_Regex_VOR.csv",row.names=FALSE) #68 ##(DONE: LINK TO NAVAID FOR NEXT STEP)##

```

## Cleaning Remaining Files from Standardized Dataset
```{r grace}
# file <- "std_missing_30_ALLROWS.csv"
# std <- read.csv(file,header = TRUE, stringsAsFactors = FALSE, na.strings=c("NA","N/A","","na","Na","n/a","N/a","NaN","nA"))
# setDT(std)
# 
# # Extract all locations marked VOR (to use NAVAID dataset)
# pattern <- c("VOR","vor")
# std$REMARKS <- gsub("RIS","RIS VOR",std$REMARKS) #RIS is Riverside VOR in MO
# std$REMARKS <- gsub("CQO","CQO VOR",std$REMARKS) #CQO is Choo Choo VOR in TN #Different Source says GQO
# std$REMARKS <- gsub("WASATEC","TCH",std$REMARKS) #TCH is Wasatch VOR in UT #REMARKS MISPELLED
# std_vor <- std[grep(paste(pattern,collapse="|"),std$REMARKS)] #3 (DIVE DEEPER)
#   # Attempt to find XXX NM XXX of XXX format (OUT OF 13)
#   std_vor$UASLOCATION <- str_extract(std_vor$REMARKS,'[0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*\\s?(nm|NM)\\s? (NORTH|SOUTH|EAST|WEST|(N|n)orth|(S|s)outh|(E|e)ast|(W|w)est|N|S|E|W|n|s|e|w|NW|NE|SW|SE|nw|ne|sw|se|SSE|SSW|SNE|SNW|NNE|NSE|NNE|NNW|WSW|WNW|WSE|WNE|ENE|ESE|ESW|ENW|sse|ssw|sne|snw|nne|nnw|wsw|wnw|wse|wne|ene|ese|esw|enw)*(\\s?(of|OF)\\s?[A-Z]{3,4})')
#   std_vor$DATASET <- "NAVAID"
#   std_vor$UASLOCATION <- gsub("([0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*)(NM)","\\1 \\2",std_vor$UASLOCATION)
#   std_completed <- std_vor #3
#   
# ##---->       MISSING STANDARD INCIDENTS with VOR DATASET##
#     write.csv(std_vor,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\6.3-MissingStandard_Incidents_VOR.csv",row.names=FALSE) #14 #DONE  
#   
# std <- std[!grep(paste(pattern,collapse="|"),std$REMARKS)]    #27 (DIVE DEEPER {RWY AND REGULAR})
#   # Extract all locations marked RWY (to use RUNWAY dataset)
#   std_rwy <- std[grepl("RWY",std$REMARKS)] #14
#   std_rwy$DATASET <- "AIRPORT/RUNWAY"
#     # Attempt to find XXX NM XXX of XXX format (OUT OF 14)
#     std_rwy$UASLOCATION <- str_extract(std_rwy$REMARKS,'[0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*\\s?(nm|NM)\\s? (NORTH|SOUTH|EAST|WEST|(N|n)orth|(S|s)outh|(E|e)ast|(W|w)est|N|S|E|W|n|s|e|w|NW|NE|SW|SE|nw|ne|sw|se|SSE|SSW|SNE|SNW|NNE|NSE|NNE|NNW|WSW|WNW|WSE|WNE|ENE|ESE|ESW|ENW|sse|ssw|sne|snw|nne|nnw|wsw|wnw|wse|wne|ene|ese|esw|enw)*(\\s?(of|OF))')
#     # Extract all NA locations (OUT OF 8563)
#     std2_rwy_na <- std_rwy[is.na(std_rwy$UASLOCATION)] #0
#     std2_rwy <- std_rwy[!is.na(std_rwy$UASLOCATION)] #13
#       std2_rwy$UASLOCATION <- gsub("([0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*)(NM)","\\1 \\2",std2_rwy$UASLOCATION)
#       std2_rwy$UASLOCATION <- gsub("([A-Z]{1,3})(of)","\\1 \\2",std2_rwy$UASLOCATION)
#       std2_rwy$UASLOCATION <- paste(std2_rwy$UASLOCATION,std2_rwy$REPORTINGFACILITY)
#         # SIG is Puerto Rico Airport
#         # END is AFB
#         std$REMARKS <- gsub("L30","LAS",std$REMARKS) #L30 is AREA, LAS is Airport
#       std2_rwy$RWYLOCATION <- str_extract(std2_rwy$REMARKS,'RWY\\s?[0-9]{1,2}[L|R|C]?')
#       std2_rwy$RWYLOCATION <- gsub("(RWY)([0-9]{1,2})","\\1 \\2",std2_rwy$RWYLOCATION)
#       std2_rwy$RWYLOCATION <- gsub("(RWY\\s)(8|9)","\\10\\2",std2_rwy$RWYLOCATION)
#       std_completed <- rbind(std_completed,std2_rwy, fill=TRUE) #17
#       
# ##---->       MISSING STANDARD INCIDENTS with RUNWAYS DATASET##
#     write.csv(std2_rwy,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\6.2-MissingStandard_Incidents_RWY.csv",row.names=FALSE) #14 #DONE
#   
#   # Extract all other locations 
#   std <- std[!grepl("RWY",std$REMARKS)] #13
#   std$DATASET <- "AIRPORT"
#     # Attempt to find XXX NM XXX of XXX format (OUT OF 13)
#     #OUC - PAMLICO NDB Lat/Long 35°9'30.60"N, 76°45'45.73"W
#     #BEQ - BESSEMER NDB (EKY) Lat/Long 33°18'45.40"N, 86°55'34.70"W
#     #BURDY (waypoint) Lat/long 	41°57'19.140"N, 70°57'07.450"W
#     #CEDES (waypoint) Lat/long 	37°33'02.960"N, 121°37'28.510"W
#     #HSN ??? - Taking from Reporting Facility
#     #HUB ??? - Taking from Most Likely, HOU
#     std$REMARKS <- gsub("FTG","CFO",std$REMARKS) #OUTDATED CODE
#     std$REMARKS <- gsub("XXX","FFZ",std$REMARKS) #MISSING CODE FROM REPORTING FACILITY
#     std$REMARKS <- gsub("UOA","UAO",std$REMARKS) #TYPO, FROM REPORTING FACILITY
#     std$REMARKS <- gsub("DEM","DEN",std$REMARKS) #MOST LIKELY TYPO ## D01 IS AREA, DEN IS FACILITY
#     std$REMARKS <- gsub("HUB","HOU",std$REMARKS) #I09 is AREA, HOU IS MOST LIKELY FACILITY
#     std$REMARKS <- gsub("HEMET","HMT",std$REMARKS) #HEMET IS NAME OF AIRPORT, HMT IS CODE
#     std$REMARKS <- gsub("HSN","OKC",std$REMARKS) #FROM REPORTING FACILITY
#     std$REMARKS <- gsub("LIV","LKV",std$REMARKS) #TYPO, FROM PD NOTIF
#     std$REMARKS <- gsub("BEQ","EKY",std$REMARKS) #From OPENNAV
#     std$UASLOCATION <- str_extract(std$REMARKS,'[0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*\\s?(nm|NM)\\s? (NORTH|SOUTH|EAST|WEST|(N|n)orth|(S|s)outh|(E|e)ast|(W|w)est|N|S|E|W|n|s|e|w|NW|NE|SW|SE|nw|ne|sw|se|SSE|SSW|SNE|SNW|NNE|NSE|NNE|NNW|WSW|WNW|WSE|WNE|ENE|ESE|ESW|ENW|sse|ssw|sne|snw|nne|nnw|wsw|wnw|wse|wne|ene|ese|esw|enw)*(\\s?(of|OF)\\s?[A-Z]{3,5})')
#     # Extract all NA locations (OUT OF 8563)
#     std2_na <- std[is.na(std$UASLOCATION)] #0
#     std2 <- std[!is.na(std$UASLOCATION)] #13
#       std2$UASLOCATION <- gsub("([0-9]*\\-*\\/*[0-9]*\\.*[0-9]\\.*[0-9]*)(NM)","\\1 \\2",std2$UASLOCATION)
#       pattern <- c("BURDY","CEDES")
#       std3 <- std2[!grep(paste(pattern,collapse="|"),std2$REMARKS)] #11
#       std_completed <- rbind(std_completed,std3, fill=TRUE) #28
#     
# ##---->       MISSING STANDARD INCIDENTS with FULL FORMAT DATASET##
#         write.csv(std3,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\6.1-MissingStandard_Incidents_AIRPORT_FULLFORMAT.csv",row.names=FALSE) #11 #DONE
#       std_waypoint <- std2[grep(paste(pattern,collapse="|"),std2$REMARKS)] #2
#       std_waypoint$waypoint_lat <- c("41° 57' 19.140\" N","37° 33' 02.960\" N")
#       std_waypoint$waypoint_long <- c("86° 55' 34.70\" W","121° 37' 28.510\" W")
#       std_waypoint$DATASET <- "LAT/LONG PROVIDED"
#       std_completed <- rbind(std_completed,std_waypoint, fill=TRUE) #30
#     
# ##---->       MISSING STANDARD INCIDENTS with WAYPOINTS DATASET##
#       write.csv(std_waypoint,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\6.4-MissingStandard_Incidents_AIRPORT_WAYPOINTS.csv",row.names=FALSE) #2 DONE
#       
# std_completed <- arrange(std_completed,DATE)
# #Remove Duplicates (same sighting/different callsign or time)
# std_completed <- distinct(std_completed,dateonly,UASLOCATION,.keep_all=TRUE) #68
#   write.csv(std_completed,"C:\\Users\\maygo\\OneDrive\\Documents\\DAEN690-FAA-UAS\\06-MissingStandard_Incidents_AIRPORT.csv",row.names=FALSE) #30 #DONE    

```